Static survey

### 2023-05-16 notebook/survey-static.qmd
Add all files related to original survey

---
title: "Survey questions"
---

@@

:   Dropdown menu with [country names from the World Bank](/project/diss-ingos-in-autocracies/survey-countries/).

    Though dropdown menus are poor UI, [adding an autocomplete field to Qualtrics is doable](/project/diss-ingos-in-autocracies/survey-notes/), but tricky and won't always work consistently (e.g. if a respondent disables JavaScript, validating their response nearly impossible since they'll have to type the name of the country in blindly—and perfectly—to make it match the validating regex).

@@

    Horrible nasty UX here, but ¯\\\_(ツ)\_/¯. There's no good way to do this in Qualtrics

@@

Enable "Loop and merge" for this block. Respondents can fill out this section as many times as they want for each of the countries they work in.

[Qualtrics' solution for complicated looping and merging is pretty kludgy](https://support.qualtrics.com/survey-platform/edit-survey/block-options/loop-and-merge#LoopingBasedOnAYesNo). Respondents can repeat this block up to 5 times (regardless of how many countries they work in). The final question of this block, Q4.24, lets respondents either restart the block or continue to the next block.

In order to end the cycle of loops early, **each question in this block** needs to have display logic hiding itself if the respondent chooses to end the loop:

![Display logic for every question in the looped block](/files/images/survey-loop-display-logic.png){.pure-img-responsive}

It's a mess, but it works.

@@

:   Matrix table

@@

    |                                                     | A great deal | A lot | A moderate amount | A little | Not at all | Don't know | Not applicable |
    | --------------------------------------------------- | :----------: | :---: | :---------------: | :------: | :--------: | :--------: | :------------: |
    | Regulations regarding registration                  |      •       |   •   |         •         |    •     |     •      |     •      |       •        |
    | Regulations regarding operations                    |      •       |   •   |         •         |    •     |     •      |     •      |       •        |
    | Regulations regarding speech and advocacy           |      •       |   •   |         •         |    •     |     •      |     •      |       •        |
    | Regulations regarding communication and cooperation |      •       |   •   |         •         |    •     |     •      |     •      |       •        |
    | Regulations regarding assembly                      |      •       |   •   |         •         |    •     |     •      |     •      |       •        |
    | Regulations regarding resources                     |      •       |   •   |         •         |    •     |     •      |     •      |       •        |

*Q4.16a*: Please describe how your organization is affected by regulations regarding registration.

    Only display if corresponding response in Q4.16 is "A great deal", "A lot", "A moderate amount", or "A little"

*Q4.16b*: Please describe how your organization is affected by regulations regarding operations.

    Only display if corresponding response in Q4.16 is "A great deal", "A lot", "A moderate amount", or "A little"

*Q4.16c*: Please describe how your organization is affected by regulations regarding speech and advocacy.

    Only display if corresponding response in Q4.16 is "A great deal", "A lot", "A moderate amount", or "A little"

*Q4.16d*: Please describe how your organization is affected by regulations regarding communication and cooperation.

    Only display if corresponding response in Q4.16 is "A great deal", "A lot", "A moderate amount", or "A little"

*Q4.16e*: Please describe how your organization is affected by regulations regarding assembly.

    Only display if corresponding response in Q4.16 is "A great deal", "A lot", "A moderate amount", or "A little"

*Q4.16f*: Please describe how your organization is affected by regulations regarding resources.

    Only display if corresponding response in Q4.16 is "A great deal", "A lot", "A moderate amount", or "A little"

@@

:   Matrix table

    |                                                   | Yes |  No | Don’t know | Not applicable |
    | ------------------------------------------------- | :-: | :-: | :--------: | :------------: |
    | We changed the sources of our funding             |  •  |  •  |     •      |       •        |
    | We changed which issues we work on                |  •  |  •  |     •      |       •        |
    | We changed how we communicate with the government |  •  |  •  |     •      |       •        |
    | We changed how we communicate with our donors     |  •  |  •  |     •      |       •        |
    | We changed which locations we work in             |  •  |  •  |     •      |       •        |
    | We changed the location of our country office     |  •  |  •  |     •      |       •        |
    | We used more local staff and/or volunteers        |  •  |  •  |     •      |       •        |
    | We used more foreign staff and/or volunteers      |  •  |  •  |     •      |       •        |

*Q4.21a*: Please describe how your organization changed its funding sources. What regulation were you responding to?

    Display if corresponding answer in Q4.21 is "Yes"

*Q4.21b*: Please describe how your organization changed which issues it works on. What regulation were you responding to?

    Display if corresponding answer in Q4.21 is "Yes"

*Q4.21c*: Please describe how your organization changed how it communicates with the government. What regulation were you responding to?

    Display if corresponding answer in Q4.21 is "Yes"

*Q4.21d*: Please describe how your organization changed how it communicates with donors. What regulation were you responding to?

    Display if corresponding answer in Q4.21 is "Yes"

*Q4.21e*: Please describe how your organization changed the locations it works in. What regulation were you responding to?

    Display if corresponding answer in Q4.21 is "Yes"

*Q4.21f*: Please describe how your organization changed the location of its country office. What regulation were you responding to?

    Display if corresponding answer in Q4.21 is "Yes"

*Q4.21g*: Please describe how your organization used more local staff or volunteers. What regulation were you responding to?

    Display if corresponding answer in Q4.21 is "Yes"

*Q4.21h*: Please describe how your organization used more foreign staff or volunteers. What regulation were you responding to?

    Display if corresponding answer in Q4.21 is "Yes"

@@

*Q4.24*: That's all I need to know about your organization's work in `target_country`.<br><br>You can either answer the same set of questions for another country your organization works in (this would be helpful) or move on to the survey's final questions.

@@

*Q7.1*: This survey is only concerned with international NGOs, or NGOs that work in countries other than the ones they are based in. Based on your responses, your organization only works in `home_country`, indicating that you are not an international NGO.<br><br>If this is a mistake and your organization does work abroad, click here to restart the survey. Otherwise, click on the forward arrow below to end the survey.<br><br>Thanks for your time!

>>>>

---
title: "Static survey"
---

@@

:   Dropdown menu with [country names from the World Bank](/notebook/survey-countries.qmd).

@@

@@

Respondents can fill out this section as many times as they want for each of the countries they work in.

@@

@@

    |                                                     | A great deal | A lot | A moderate amount | A little | Not at all | Don't know | Not applicable | Please explain briefly |
    | --------------------------------------------------- | :----------: | :---: | :---------------: | :------: | :--------: | :--------: | :------------: | :--------------------: |
    | Regulations regarding registration                  |      •       |   •   |         •         |    •     |     •      |     •      |       •        |       Text field       |
    | Regulations regarding operations                    |      •       |   •   |         •         |    •     |     •      |     •      |       •        |       Text field       |
    | Regulations regarding speech and advocacy           |      •       |   •   |         •         |    •     |     •      |     •      |       •        |       Text field       |
    | Regulations regarding communication and cooperation |      •       |   •   |         •         |    •     |     •      |     •      |       •        |       Text field       |
    | Regulations regarding assembly                      |      •       |   •   |         •         |    •     |     •      |     •      |       •        |       Text field       |
    | Regulations regarding resources                     |      •       |   •   |         •         |    •     |     •      |     •      |       •        |       Text field       |

@@

    |                                                   | Yes |  No | Don’t know | Not applicable | Please explain briefly |
    | ------------------------------------------------- | :-: | :-: | :--------: | :------------: | :--------------------: |
    | We changed the sources of our funding             |  •  |  •  |     •      |       •        |       Text field       |
    | We changed which issues we work on                |  •  |  •  |     •      |       •        |       Text field       |
    | We changed how we communicate with the government |  •  |  •  |     •      |       •        |       Text field       |
    | We changed how we communicate with our donors     |  •  |  •  |     •      |       •        |       Text field       |
    | We changed which locations we work in             |  •  |  •  |     •      |       •        |       Text field       |
    | We changed the location of our country office     |  •  |  •  |     •      |       •        |       Text field       |
    | We used more local staff and/or volunteers        |  •  |  •  |     •      |       •        |       Text field       |
    | We used more foreign staff and/or volunteers      |  •  |  •  |     •      |       •        |       Text field       |

@@

*Q4.24*: That's all I need to know about your organization's work in `target_country`. You can either answer the same set of questions for another country your organization works in (this would be helpful) or move on to the survey's final questions.

@@

*Q7.1*: This survey is only concerned with international NGOs, or NGOs that work in countries other than the ones they are based in. Based on your responses, your organization only works in `home_country`, indicating that you are not an international NGO.  
If this is a mistake and your organization does work abroad, click here to restart the survey. Otherwise, click on the forward arrow below to end the survey.  
Thanks for your time!
